Basic regression in Gaussian processes

### 2019-11-05 notebook/complete-discrete-version.Rmd
longer run

```{r}
mdp_learning_ <- memoise::memoise(mdp_learning)
  learning_sim <- mdp_learning_(transition, reward, discount, 
                      x0 = x0, 
                      Tmax = 20, 
                      true_transition = transition[[true_i]],
                      model_prior = prior,
                      type = "value iteration", 
                      epsilon = 1e-2)

@@

@@

```{r}
 learning_sim$posterior %>% 
  data.frame(time = 1:Tmax) %>%
  filter(time %in% seq(1,Tmax, by = 5)) %>%
  gather(param, probability, -time, factor_key =TRUE) %>% 
  mutate(param = possible_a[as.integer(param)]) %>% 
  ggplot(aes(param, probability, group = time, alpha = time)) + 
  geom_line()
```

>>>>

```{r}
set.seed(12345)
Tmax_learning <- 500
mdp_learning_ <- memoise::memoise(mdp_learning)
  learning_sim <- mdp_learning_(transition, reward, discount, 
                      x0 = x0, 
                      Tmax = Tmax_learning, 
                      true_transition = transition[[true_i]],
                      model_prior = prior,
                      type = "value iteration", 
                      epsilon = 1e-2)

@@

```{r}
saveRDS(learning_sim, "learning_sim.rds")
```

@@

```{r}
 learning_sim$posterior %>% 
  data.frame(time = 1:Tmax_learning) %>%
  filter(time %in% seq(1,Tmax_learning, by = 5)) %>%
  gather(param, probability, -time, factor_key =TRUE) %>% 
  mutate(param = possible_a[as.integer(param)]) %>% 
  ggplot(aes(param, probability, group = time, alpha = time)) + 
  geom_line()
```
